Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 ms.tex
some systematic words

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new publicly available, general-purpose implementation 
of the \citet{Morton12} procedure,
to calculate false positive probabilities (FPPs) for each of these
\KT\ candidates.  We impose the following constraints on false positive
scenarios:
\begin{itemize}
\item A chance-aligned eclipsing binary system may reside anywhere inside
or within one pixel of the photometric aperture of the target star.
\item The maximum allowed depth of a potential secondary eclipse event
is the most significantly detected signal at the same
period of the planet candidate, once the primary transit is masked out.
\item Blended stars must be allowed by the available adaptive optics
and archival imaging data (discussed in detail below).
\end{itemize}

@@

We find that four of the presented candidates have FPP $>$90\%;
these we consider to be likely false positives.
On the other hand, we find that 21 candidates
have FPP $<$ 1\%.  
Two of these we find to be caused by systematics
in the transit search noise model (details in \S\ref{sec:systematics}), and
so we identify those as false positives.  
Four more of these 21 might plausibly be caused by 
contamination by detected stellar companions within the photometric apertures 
(see \S\ref{sec:background}), so we keep these as candidates.

@@

\subsection{Two Candidates, One Ephemeris}
\label{sec:ephemmatch}

EPIC 201569483 was originally listed in \paperit\ as a planet candidate.
The transit events have a depth of approximately 7\%.
In this work, we conclude this system is likely a false
positive, with an FPP of 0.560.
The most likely scenario is that of an eclipsing binary, which would
not be surprising given the transit depth.

It was later realized that EPIC 201555883 has a period, time of transit,
and transit duration consistent with EPIC 201569483.
Such effects are not uncommon in \kep\ data.
\citet{Batalha13} found $\sim 25$ planet candidates to be false positives
based on matching ephemerides between candidates.
In that paper, the authors limited their search to candidates within
$20\arcsec$ of other objects of interest.
\citet{Coughlin14} expanded on this method, identifying 685 KOIs as false
positives and outlining four physical reasons why these anomalies may occur.
As those authors explain, period-matching candidates can be the result of
direct PRF contamination, antipodal reflection across the Schmidt telescope,
CCD crosstalk across a \kep\ module, or ``column anomalies'' across one column
of the CCD.
Typically, the instrumental false positive event appears considerably
shallower than the true astrophysical event.

EPIC 201555883 is a unique case in that it does not appear to fall under any
of these cases. It falls on module 23, while EPIC 201569483 is on module 8,
neither 180 degrees away from nor on the same column as this candidate.
Moreover, there is not any evidence of a mechanism that could cause a third
star to induce both the appearance of a $7\%$ eclipse on one module and an
additional anomalous transit event on a different module.
Instead, this candidate could be a false positive caused by a different
systematic mechanism.
\paperit\ modeled the systematic effects in the \KT\ light curves using a
linear combination of ``eigen light curves'' generated empirically by running
a principle component analysis on the light curves of every star.
This means that the training set includes the light curves for variable stars,
eclipsing binaries, and even transiting planets.

Formally, our false positive validation scheme gives a FPP of $9.5 \times
10^{-4}$, reaching our threshold for planet validation.
Since \texttt{vespa} does not account for the possibility of instrumental
artifacts in the data, this number represents only the \textit{astrophysical}
false positive probability.
In this case, given the period matching between the two events, we refrain
from declaring this system a planet.
However, since we cannot explain how such a false positive would occur as a
result of an instrumental systematic in the \kep\ telescope, we also refrain
from declaring this target a definite false positive.
Additional follow-up observations of both targets are clearly warranted to
better understand a possible systematic that has not previously been observed
in either \kep\ or \KT.

\subsection{Multiple Planet Systems}
Five of the systems identified by \paperit\ are candidates to be multiply-transiting
systems.
One of these is EPIC 201367065, a three-planet system originally announced by
\citet{Crossfield15}.
Another of these is EPIC 201505350 \citep{Armstrong15b}, a two-planet system with the
orbital periods of the two planets near a 3:2 period commensurability.
The remaining three are all representative of the multiple-planet systems observed by
\kep\ \citep{Lissauer11b, Fabrycky14}.
Two of the systems are near a period commensurability and all three consist of
mini-Neptune sized planets.
Like in the \kep\ field, the false positive rate we measure for the multiple planet sample
here ($0/10$) is lower than for the single systems \citep{Lissauer12, Rowe14}.

>>>>

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new publicly available, general-purpose implementation 
of the \citet{Morton12} procedure,
to calculate false positive probabilities (FPPs) for each of these
\KT\ candidates.  
The following constraints on false positive
scenarios are imposed:
\begin{itemize}
\item A chance-aligned eclipsing binary system may reside anywhere inside
or within one pixel of the photometric aperture of the target star.
\item The maximum allowed depth of a potential secondary eclipse event
is the most significantly detected signal at the same
period of the planet candidate, once the primary transit is masked out.
\item Blended stars must be allowed by the available adaptive optics
and archival imaging data (discussed in detail below).
\end{itemize}

@@

Four of the presented candidates have FPP $>$90\%;
these are considered to be likely false positives.
On the other hand, 21 candidates
have FPP $<$ 1\%.  
Two of these are found to be caused by systematics
in the transit search noise model (details in \S\ref{sec:systematics}), and
so we identify those as false positives.  
Four more of these 21 might plausibly be caused by 
contamination by detected stellar companions within the photometric apertures 
(see \S\ref{sec:background}), so we keep these as candidates.

@@

\subsection{Non-Astrophysical False Positives}
\label{sec:systematics}

The method of \paperit assumes that all variability in the light curves are
caused by either the motion of \KT, in which case the variability is shared
by all stars, or transits of planets, in which case the variability is intrinsic 
to only one star.
This assumption breaks down for extremely spotted stars where the 
astrophysical variability is larger than the instrumental
magnitude.
In that regime, the starspot modulations can be incorrectly fit by the 
systematic model, causing spurious transits to appear.
This appears to be the case with EPIC 201929294, which has 
coherent starspots that appear to have the same rotation period as the
transit period reported previously.
Because the starspots are so periodic and coherent, these spurious 
transits were falsely identified as a planet candidate; we consider that 
system a false positive in this work.

The planet candidate possibly orbiting EPIC 201555883 has a period, 
time of transit, and transit duration consistent with EPIC 201569483.
Such effects are not uncommon in \kep\ data.
\citet{Coughlin14} identify 685 KOIs as false
positives and outline four physical reasons why these anomalies may occur.
EPIC 201555883 is a unique case in that it does not appear to fall under any
of these cases. It falls on module 23, while EPIC 201569483 is on module 8,
neither 180 degrees away from nor on the same column as this candidate.
Moreover, there is not any evidence of a mechanism that could cause a third
star to induce both the appearance of a $7\%$ eclipse on one module and an
additional anomalous transit event on a different module.
Instead, this candidate could be a false positive caused by a different
systematic mechanism.
\paperit\ modeled the systematic effects in the \KT\ light curves using a
linear combination of ``eigen light curves'' generated empirically by running
a principle component analysis on the light curves of every star.
This means that the training set includes the light curves for variable stars,
eclipsing binaries, and even transiting planets.
In this specific case, the s

\subsection{Multiple Planet Systems}
Five of the systems identified by \paperit\ are candidates to be multiply-transiting
systems.
One of these is EPIC 201367065, a three-planet system originally announced by
\citet{Crossfield15}.
Another of these is EPIC 201505350 \citep{Armstrong15b}, a two-planet system with the
orbital periods of the two planets near a 3:2 period commensurability.
The remaining three are all representative of the multiple-planet systems observed by
\kep\ \citep{Lissauer11b, Fabrycky14}.
Two of the systems are near a period commensurability and all three consist of
mini-Neptune sized planets.
